### 2023-03-27 main/chapter_2ljets.tex
add background feynman diagrams

>>>>

Any sensitivity to these signals requires them to be visible above the
background noise.
For our purposes, that background noise arises from known processes of the
Standard Model.
After selecting parts of data that are sensitive to our C1N2 and GMSB signals,
it turns out that the most important backgrounds are describable as
$ZZ$-like \diboson,
$\zyjets$,
or $\ttbar$;
these processes are illustrated in Figure~\ref{fig:2ljets_feynman}.
Each of these Standard Model processes produces visible lepton pairs, jets, and
missing transverse momentum to mimic our signal models' effects.
Although $\zyjets$ events lack prompt invisible particles for missing
transverse momentum, this is offset by its large production cross-section
with missing transverse momentum sourced from indirect effects such as
mismeasured jets.

% background diagrams
\begin{figure}[tp]
\centering
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_feynman_diboson_zz.png}
\caption{$ZZ$-like \diboson}
\end{subfigure}
\hfill
\begin{subfigure}{0.46\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_feynman_zyjets_slash.png}
\caption{$\zyjets$}
\end{subfigure}
\\
\begin{subfigure}{0.4\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_feynman_ttbar.png}
\caption{$\ttbar$}
\end{subfigure}
\hfill
\begin{subfigure}{0.46\textwidth}
\centering
\includegraphics[width=\textwidth]{figures/2ljets_feynman_top_decay.png}
\caption{Top quark decay}
\end{subfigure}
\caption[
Feynman diagrams for the Standard Model background processes
]{%
Feynman diagrams for the Standard Model background processes of important
background contributions in the $\twoljets$-electroweak search.
In \diboson\ events we expect one $Z$ boson-like decay to charged leptons, and
the other to neutrinos; additional jets can arise from initial state radiation
or additional strong radiations from the hard scatter.
Missing transverse momentum is absent from prompt emissions in $\zyjets$
events, as illustrated in (b), but arises from rare mismeasurements or
non-prompt decays.
Top quarks rapidly decay weakly, mainly to $b$-flavoured hadrons due to the
small weak mixing with the third generation;
panel (d) illustrates this with a leptonic decay that we expect to select.
}
\label{fig:2ljets_feynman}
\end{figure}
